Summary of antibiotic consumption

### 2017-02-22 hicks-summary/hicks-summary.Rmd
refactor hicks

```{r setup, echo=FALSE}
library(assertive)

@@

```{r load_db, echo=FALSE, message=FALSE}

regions = read_tsv('../../../db/census-regions/census-regions.tsv') %>%
  select(state, region)

antibiotic_class = read_tsv('../../abx_class.tsv') %>%
  select(antibiotic, antibiotic_class) %>%
  distinct

@@

```{r analyze_data, cache=TRUE, echo=FALSE, message=FALSE}
analyze = function(this_year) {
  bene = read_tsv(sprintf('../../bene_%i.tsv', this_year)) %>%
    mutate_at(vars(age, plan_coverage_months), as.integer) %>%
    filter(!is.na(state), plan_coverage_months == 12, age >= 65) %>%
    left_join(regions, by='state')

@@

  pde = read_tsv(sprintf('../../pde_%i.tsv', this_year)) %>%
    mutate_at(vars(days_supply), as.integer) %>%
    left_join(antibiotic_class, by='antibiotic')

@@

```{r arrange_data, echo=FALSE}
library(knitr)
data = list("2011"=data_2011,
            "2012"=data_2012,
            "2013"=data_2013,
            "2014"=data_2014)

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```

```{r setup}
library(assertive)

@@

```{r load_db}

regions = read_tsv('../../db/census-regions/census-regions.tsv') %>%
  select(state, region)

antibiotic_class = read_tsv('../abx_class.tsv') %>%
  select(antibiotic, antibiotic_class) %>%
  distinct

@@

```{r analyze_data, cache=TRUE}
analyze = function(this_year) {
  bene = read_tsv(sprintf('../bene_%i.tsv', this_year)) %>%
    mutate_at(vars(age, plan_coverage_months), as.integer) %>%
    filter(!is.na(state), plan_coverage_months == 12, age >= 65) %>%
    left_join(regions, by='state')

@@

  pde = read_tsv(sprintf('../pde_%i.tsv', this_year)) %>%
    mutate_at(vars(days_supply), as.integer) %>%
    left_join(antibiotic_class, by='antibiotic')

@@

```{r arrange_data}
library(knitr)
data = list("2011"=data_2011,
            "2012"=data_2012,
            "2013"=data_2013,
            "2014"=data_2014)
